Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-22 paper/ijcai/paper.tex
restruturação

\begin{itemize}[leftmargin=0em]
\item[]{\textbf{RQ1.}}~\textit{\rqone{}}
\item[]{\textbf{RQ2.}}~\textit{\rqtwo{}}
\item[]{\textbf{RQ2.}}~\textit{\rqthree{}}
\end{itemize}

@@

Figure~\ref{fig:foos} shows the predominance of Fault Of Omission (FOO) cases in
the dataset, i.e., faults which generally are difficult to locate. $59.7\%$ of
the faults of this dataset are FOOs.

@@

\subsection{Dynamic Slicing}\label{sec:ds}

This subsection aims to report the performance of the \ds{} technique on slicing de
faults of $5$ \dfj{} projects. Table \ref{tab:red}
presents the reduction percentage obtained for each project after slicing the top
$5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction
of 30.23\% in the projects considered in our study.

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lcc}
		\toprule
		Project             &  \combpar{5}  & \combpar{10} \\
		\midrule

@@

In this section, we answer the research questions proposed and discuss the
results obtained. Our approach was capable of slicing a total of $260$ faults
from $5$ different  projects. The remaining faults were not considered because
(1) faults belong to the \closure{} project which requires high CPU to perform
the \combpar{k} evaluation  or (2) faults whose test outputs were not
reproducible in the machine used to run the experiments. \textbf{RQ1} reviews
one of the main issues of \ds{} - missing faulty statements - whereas
\textbf{RQ2} discusses how effective is the \combpar{k} approach against
\sfl{}$^{k}$.

\subsubsection{RQ1: \textit{How often does \ds{} misses faulty statements?}}
\label{sec:fault-misses}

@@

\subsubsection{RQ2: \textit{How effective is the \combpar{k} combination for bug localization?}}

>>>>

\begin{itemize}[leftmargin=0em]
\item[]{\textbf{RQ1.}}~\textit{\rqone{}}
\item[]{\textbf{RQ2.}}~\textit{\rqtwo{}}
\item[]{\textbf{RQ3.}}~\textit{\rqthree{}}
\end{itemize}

@@

Figure~\ref{fig:foos} shows the predominance of Fault Of Omission (FOO) cases in
the dataset, i.e., faults which generally are difficult to locate. $59.7\%$ of
the faults of this dataset are FOOs. \Sof{@todo: Explain better what are FOOs}

@@

@@

In this section, we answer the research questions proposed and discuss the
results obtained. Our approach was capable of slicing a total of $260$ faults
from $5$ different  projects. The remaining faults were not considered because
(1) faults belong to the \closure{} project which requires high CPU to perform
the \combpar{k} evaluation  or (2) faults whose test outputs were not
reproducible in the machine used to run the experiments. \textbf{RQ1} evaluates how effective is \ds{} on reducing the test cases, \textbf{RQ2} reviews
one of the main issues of \ds{} - missing faulty statements - and
\textbf{RQ3} discusses how effective is the \combpar{k} approach against
\sfl{}$^{k}$.

\subsubsection{RQ1: \textit{\rqone}}
\label{rq:1}

This subsection aims to report the performance of the \ds{} technique on slicing de
faults of $5$ \dfj{} projects. Table \ref{tab:red}
presents the reduction percentage obtained for each project after slicing the top
$5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction
of $30.23\%$ in the projects considered in our study.

\begin{table}[H]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lcc}
		\toprule
		Project             &  \combpar{5}  & \combpar{10} \\
		\midrule

\subsubsection{RQ2: \textit{\rqtwo}}
\label{rq:2}

@@

\subsubsection{RQ3: \textit{\rqthree}}
